---
title: "R Markdown and Leaflet"
author: "Nati Munoz"
date: "30/06/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE)
```

## Introduction

As part of the "Developing Data Products" course in coursera we will build an html page with an interactive map. The map will be from London and will highlight 3 of its main attractions.

Before we can build the map we need to isntall the leaflet package and library.

```{r , echo=FALSE}
install.packages("leaflet",repos = "http://cran.us.r-project.org")
library(leaflet)
```

## Creation of the map

The leaflet function will create a world map so I will give some coordinates to show only London. The coordinates are passed as a parameter by building a dataframe with the latitude, longitud and name of the points to show in the map.

```{r, echo=FALSE}

map <- data.frame(lat= c(51.503399,51.504501, 51.500942), lng= c(-0.119519, -0.086500, -0.177498))
name <- c("London Eye", "The Shard", "Royal Albert Hall")

map  %>% 
  leaflet() %>% 
  addTiles()%>% 
  addMarkers(popup= name)
map

```

